Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2021-01-05 xrb2/paper.tex
Updated Section 3.2
- Expanded explanation of position vs. time fitting procedure
- Switched s_0 to v_0 in flame speeds table (being somewhat pedantic,
  but s_0 was negative for the 3e8 K run)
- Added note on v_0 vs. actual initial velocity
- Tentatively suggested baroclinicity plot

Burning in the {\tt F500} and {\tt F1000} runs is concentrated in a dense region with circular motion. Figure \ref{fig:urho} compares the horizontal $x$-velocity $u$, density $\rho$ and the nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the {\tt F250}, {\tt F500}, and {\tt F1000} runs. Most of the burning for each of the simulations occurs in a high density region $\rho > 3 \times 10^5 {\rm g\,cm^{-3}}$. The fluid in this dense, high energy generation region undergoes vortical motion, shown in the Figure \ref{fig:uv} phase plots comparing $u$, $v$ and $\dot{e}_{\rm nuc}$. From the previous plots (see: streamlines?) \MarginPar{NF: need to add streamline plots?}, this most likely corresponds to the leading edge of the flame where fresh fuel is being entrained. This feature is not developed in the 250~Hz flame; it could potentially develop at later times (past the point at which we terminated our simulation), or the flame could just fizzle out and fail to ignite entirely.

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each 
	simulation. $s_0$ is the speed at $t = 0$. The initial flame velocities and accelerations are 
	derived from a quadratic least-squares fit to each of the datasets for times $t \gtrsim 
	20~\mathrm{ms}$.}
	\tablehead{\colhead{run} & \colhead{$s_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
  {\tt F1000}     & $(3.38 \pm 0.11) \times 10^5$ & $(-0.43 \pm 1.57) \times 10^5$ \\
  {\tt F500}      & $(2.66 \pm 0.27) \times 10^5$ & $(10.97 \pm 3.22) \times 10^5$ \\
  {\tt F500\_2E8} & $(3.98 \pm 0.19) \times 10^5$ & $(-1.56 \pm 2.63) \times 10^5$ \\
  {\tt F500\_3E8} & $(-4.56 \pm 2.92) \times 10^5$ & $(3.39 \pm 0.60) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}

@@

Figure~\ref{fig:flame_speeds_1} gives position vs.\ time for the $\tt{F500}$ and $\tt{F1000}$ runs 
(blue and orange, respectively) to show the dependence on rotation rate. As some of the hotter 
500~Hz runs exhibit significant acceleration, we fit a quadratic curve to each set of data for 
times $t \gtrsim 20~\mathrm{ms}$, with the fit parameters giving the flame acceleration and 
initial velocity. \MarginPar{KE: Can add an explanation of the averaging method once that's 
decided.} These results are displayed in Table~\ref{table:flame_speeds}. \MarginPar{NF: I will 
update the error estimates.}

@@

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$. Note that due to its rapid acceleration, $\tt{F500\_3E8}$ 
		(orange) is only run out to $\sim 0.07~\mathrm{s}$ to avoid surpassing the domain boundary.}
\end{figure}

>>>>

Burning in the {\tt F500} and {\tt F1000} runs is concentrated in a dense region with circular 
motion. Figure \ref{fig:urho} compares the horizontal $x$-velocity $u$, density $\rho$ and the 
nuclear energy generation rate $\dot{e}_{\rm nuc}$ for the {\tt F250}, {\tt F500}, and {\tt F1000} 
runs. Most of the burning for each of the simulations occurs in a high density region $\rho > 3 
\times 10^5 {\rm g\,cm^{-3}}$. The fluid in this dense, high energy generation region undergoes 
vortical motion, shown in the Figure \ref{fig:uv} phase plots comparing $u$, $v$ and $\dot{e}_{\rm 
nuc}$. From the previous plots (see: streamlines/baroclinicity?) \MarginPar{NF: need to add 
streamline plots?}, this most likely corresponds to the leading edge of the flame where fresh fuel 
is being entrained. This feature is not developed in the 250~Hz flame; it could potentially develop 
at later times (past the point at which we terminated our simulation), or the flame could just 
fizzle out and fail to ignite entirely.

@@

\begin{deluxetable}{lrrr}
	\tablecaption{\label{table:flame_speeds} Flame speed and acceleration values measured for each 
	simulation. {\color{blue}$v_0$} is the flame velocity {\color{blue}in the $+r$ direction} at $t 
	= 0$. The initial flame 
	velocities and accelerations are derived from a quadratic least-squares fit to each of the 
	datasets for times $t \gtrsim 20~\mathrm{ms}$.}
	\tablehead{\colhead{run} & \colhead{$v_0$ (cm s$^{-1}$)} & \colhead{$a$ (cm s$^{-2}$)}} 
	\startdata
  {\tt F1000}     & $(3.38 \pm 0.11) \times 10^5$ & $(-0.43 \pm 1.57) \times 10^5$ \\
  {\tt F500}      & $(2.66 \pm 0.27) \times 10^5$ & $(10.97 \pm 3.22) \times 10^5$ \\
  {\tt F500\_2E8} & $(3.98 \pm 0.19) \times 10^5$ & $(-1.56 \pm 2.63) \times 10^5$ \\
  {\tt F500\_3E8} & $(-4.56 \pm 2.92) \times 10^5$ & $(3.39 \pm 0.60) \times 10^7$ \\
	\enddata
	%
\end{deluxetable}

@@

Figure~\ref{fig:flame_speeds_1} gives position vs.\ time for the $\tt{F500}$ and $\tt{F1000}$ runs 
(blue and orange, respectively) to show the dependence on rotation rate. {\color{blue}In 
\citet{flame_wave1}, we 
used linear least-squares fits to our position vs.\ time data to estimate the propagation velocity. 
For this study we instead fit a quadratic curve to each set of data, as some of the hotter 500~Hz 
runs exhibit significant acceleration. We discard the data points with $t \lesssim 20~\mathrm{ms}$, 
since these correspond to the initial transient period before the flame has begun to propagate 
steadily.} The fit parameters yield estimates of the flame acceleration and velocity at $t = 0$, 
which are provided in Table~\ref{table:flame_speeds}. {\color{blue}Note that the listed velocity is 
only 
a parameter that may be used to calculate the flame speed at an arbitrary time. It is not an 
estimate of the true initial velocity of the flame, since the flame has not achieved ignition yet 
at $t = 0$.} \MarginPar{KE: Outside of updating the data in the table, is there anything else we 
want to add to this para?}

@@

\begin{figure}[t]
	\centering
	\plotone{500Hz_stacked_enuc1_2order.pdf}
	\caption{\label{fig:flame_speeds_2} Flame front position vs.\ time for the three 500 Hz runs with
		$T_{\mathrm{star}} \leq 3 \times 10^8~\mathrm{K}$. The dashed lines show quadratic least-squares fits to the data
		for $t \gtrsim 20~\mathrm{ms}$. Note that due to its rapid acceleration, $\tt{F500\_3E8}$ 
		(orange) is only run out to $\sim 70~\mathrm{ms}$ to avoid surpassing the domain boundary.}
\end{figure}
